\documentclass[12pt]{article}
%\usepackage{geometry}
\usepackage[a4paper,
centering,
includehead
%,showframe=true
]{geometry}

\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{courier}
\usepackage{changepage}


\usepackage{changepage}
%\usepackage[paperwidth=6in, paperheight=9in]{geometry} %For Book Printing
%==============================
\usepackage{microtype}
%==============================
%Math Related Packages
\usepackage{amsmath, amsfonts, amssymb, amsthm, xfrac, mathtools}


\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

\lstset{language=python,
basicstyle=\small\ttfamily,
xleftmargin=-2cm,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
tabsize=4,
showspaces=false,
showstringspaces=false}

\begin{document}
\begin{abstract}
This project has revolved around creating a proof checker in python. This proof checker checks proofs that are written in the Hilbert Style as seen in the book \emph{Understanding} by Klenk. It does a reasonably good job, but could also be expanded upon a great deal. Also, because this was only for a two credit class for one semester there were certain things that I was not able to do simply due to the fact that my time was limited. I will be going over what I did during this semester, some of the research that I did.
\end{abstract}

\section{QED Manifesto}
The QED Manifesto is a paper that was written in \emph{insert year} and provides an argument for the standardization of mathematical proofs. This standardization would make checking the validity of proofs much easier as it could be done with a computer program. The standardization of mathematical proofs would also have some pedagogical benefits as well. 

\section{Proof Checkers and Proof Assists}
I have looked at various proof checkers over the course of this semester, but very few of them seem to be focused on Mathematicians and what they would like to see. I am hoping that my proof checker will require minimum programming knowledge.

\section{Using the Proof Checker}
The proof checker has a simple GUI interface with load, save, and confirm validity buttons. If we click confirm validity without typing anything into the text box we see at the bottom of the screen the word \emph{Valid}. This is because a proof where not statements are made is valid. If we type in the letter \emph{a} and nothing else and press confirm validity we get \emph{Is Not Valid}. This is because we have not yet said anything about what \emph{a} is. We do not know that it is a premise. If we type in the following line 
\begin{quote}
1.  a    Pr
\end{quote}
and press confirm validity we get \emph{is valid}. In this we are making one premise and nothing else.

\begin{quote}
1.	~A\\/A				Pr
2.	A\\/(~A*B)		Pr
3.	(A\\/~A)*(A\\/B)	Dist 2
4.	A\\/~A			Simp 3
\end{quote}

\section{Applications in Teaching}
Here we will write out a proof of $x$
\begin{proof}
\end{proof}


\newpage

\begin{adjustwidth}{-2cm}{}
\begin{tabular}{ccc}
\begin{tabular}{c}
\bf{Modus Ponens (M.P.)}\\
$\dfrac{\begin{tabular}{l}$p\supset q$ \\ $p$ \end{tabular}}{/\therefore q}$\\
\end{tabular}
&
\begin{tabular}{c}
\bf{Modus Tollens (M.T.)}\\
$\dfrac{\begin{tabular}{l}$p\supset q$ \\ $\sim q$ \end{tabular}}{/\therefore \sim p}$\\
\end{tabular}
&
\begin{tabular}{c}
\bf{Hypothetical Syllogism (H.S.)}\\
$\dfrac{\begin{tabular}{l}$p\supset q$ \\ $q\supset r$ \end{tabular}}{/\therefore p \supset r}$\\
\end{tabular}\\

\begin{tabular}{c}
\bf{Simplification (Simp.)}\\
\begin{tabular}{cc}
$\dfrac{p\cdot q}{/\therefore p}$
&
$\dfrac{p\cdot q}{/\therefore q}$
\end{tabular}\\
\end{tabular}
&
\begin{tabular}{c}
\bf{Conjunction (Conj.)}\\
$\dfrac{\begin{tabular}{l}$p$ \\ $q$ \end{tabular}}{/\therefore p\cdot q}$\\
\end{tabular}
&
\begin{tabular}{c}
\bf{Dillemma (Dil.)}\\
$\dfrac{\begin{tabular}{l}$p\supset q$ \\ $r\supset s$ \\ $p\lor r$ \end{tabular}}{/\therefore q \lor s}$\\
\end{tabular}\\

\begin{tabular}{c}
\bf{Disjunctive Syllogism (D.S.)}\\
\begin{tabular}{cc}
$\dfrac{\begin{tabular}{l}$p\lor q$ \\ $\sim p$ \end{tabular}}{/\therefore q}$
&
$\dfrac{\begin{tabular}{l}$p\lor q$ \\ $\sim q$ \end{tabular}}{/\therefore p}$\\
\end{tabular}\\
\end{tabular}
&&
\begin{tabular}{c}
\bf{Addition (Add.)}\\
\begin{tabular}{cc}
$\dfrac{p}{/\therefore p\lor q}$
&
$\dfrac{q}{/\therefore p \lor q}$\\
\end{tabular}\\
\end{tabular}\\
\end{tabular}

\end{adjustwidth}


\begin{tabular}{ccc}
\begin{tabular}{c}
\bf{Double Negation (D.N.)}\\
$p :: \sim\sim p$\\
 \\
 \\
\end{tabular}
&&
\begin{tabular}{c}
\bf{Duplication (Dup.)}\\
$p :: (p\lor p)$\\
$p :: (p\cdot p)$\\
 \\
\end{tabular}\\

\begin{tabular}{c}
\bf{Commutation (Comm.}\\
$(p\lor q) :: (q\lor p)$\\
$(p\cdot q) :: (q\cdot p)$\\
 \\
\end{tabular}
&&
\begin{tabular}{c}
\bf{Association (Assoc.)}\\
$((p\lor q)\lor r) :: (p\lor (q\lor r))$\\
$((p\cdot q)\cdot r) :: (p\cdot(q\cdot r))$\\
 \\
\end{tabular}\\

\begin{tabular}{c}
\bf{Contraposition (Contrap.)}\\
$(p\supset q) :: (\sim q\supset \sim p)$\\
 \\
 \\
\end{tabular}
&&
\begin{tabular}{c}
\bf{DeMorgan's (DeM.)}\\
$\sim(p\lor q) :: (\sim p\cdot \sim q)$\\
$\sim(p\cdot q) :: (\sim p\lor \sim q)$\\
 \\
\end{tabular}\\

\begin{tabular}{c}
\bf{Biconditional Exchange (B.E.)}\\
$(p\equiv q) :: ((p\supset q)\cdot(q\supset p))$\\
 \\
 \\
\end{tabular}
&&
\begin{tabular}{c}
\bf{Conditional Exchange (C.E.)}\\
$(p\supset q) :: (\sim p\lor q)$\\
 \\
 \\
\end{tabular}\\

\begin{tabular}{c}
\bf{Distribution (Dist.)}\\
$(p\cdot(q\lor r)) :: ((p\cdot q)\lor(p\cdot r))$\\
$(p\lor (q\cdot r)) :: ((p\lor q)\cdot (p\lor r))$\\
 \\
 \\
\end{tabular}
&&
\begin{tabular}{c}
\bf{Exportation (Exp.)}\\
$((p\cdot q)\supset r) :: (p\supset(q\supset r))$\\
 \\
 \\
\end{tabular}
\end{tabular}



C. Restrictions on the Use of C.P. and I.P.
\begin{enumerate}
\item Every assumption made in a proof must eventually be discharged.
\item Once an assumption has been discharged, neither it nor any step that falls within its scope may be used in the proof again.
\item Assumptions inside the scope of other assumptions must be discharged in the reverse order in which they were made; that is, not two schope markers may cross.
\end{enumerate}
D. General Instructions for Using C.P. and I.P
\begin{enumerate}
\item For both C.P. and I.P., an assumption may be introduced at any point in the proof, provided we label it as an assumption.
\item In using C.P., we assume the antecedent of the conditional to be proved and then derive the consequent. In using I.P., we assume the opposite of what we want to prove and then derive a contradiction. All the steps from the assumption to the consequent (for C.P.) or the contradiction (for I.P.) are said to be \emph{within the scope} of the assumption.
\end{enumerate}

Quantifier Negation (Q.N.) Equivalences

\begin{enumerate}
\item $\sim(\exists x)\phi x \equiv (x)\sim\delta x$
\item $\sim(x)\phi x \equiv (\exists x)\sim\phi x$
\item $\sim(\exists x)\sim\phi x \equiv (x)\phi x$
\item $\sim (x)\sim\phi x\equiv(\exists x)\phi x$
\end{enumerate}

STATEMENT OF THE QUANTIFIER RULES, WITH ALL NECESSARY RESTRICTIONS

A. Preliminary Definitions\\
\begin{enumerate}
\item $\phi x$ is a propositional function on $x$, simple or complex. If complex it is assumed that it is enclosed in parentheses, so that the scope of any prefixed quantifier extends to the end of the formula.
\item $\phi a$ is a formula just like $\phi x$, except that every occurrence of $x$ in $\phi x$ has benn replaced by an $a$.
\item An instance of a general formula is the result of deleting the initial quantifier and replacing each variable bound by that quantifier uniformly with some name.
\item An $a$-flagged subproof is a subproof that begins with the words "flag a" and ends with some instance containing $a$.
\end{enumerate}

B. The Four Quantifier Rules


\begin{tabular}{cc}
\begin{tabular}{l}
{\bf Universal Instantiation (U.I.)}\\
 \\
$\dfrac{(x)\phi x}{/\therefore\phi a}$
\end{tabular}
&
\begin{tabular}{l}
\bf{Existential Instantiation (E.I.)}\\
 \\
\begin{tabular}{ll}
$\dfrac{(\exists x)\phi x}{/\therefore \phi a}$
&
\emph{provided we flag a}
\end{tabular}\\
\end{tabular}\\
\begin{tabular}{l}
\\
{\bf Universal Generalization (U.G.)}\\
\end{tabular}
&
\begin{tabular}{l}
\\
{\bf Existential Generalization (E.G.)}\\
 \\
$\dfrac{\phi a}{/\therefore (\exists x)\phi x}$
\end{tabular}
\end{tabular}

C. Flagging Restrictions\\
\begin{enumerate}
\item A letter being flagged must be new to the proof; that is, it may not appear, either in a formula or as a letter being flagged, previous to the step in which it gets flagged.
\item A flagged letter may not appear either in the premises or in the conclusion of a proof.
\item A flagged letter may not appear outside the subproof in which it gets flagged.
\end{enumerate}

\newpage
\lstinputlisting[language=python]{./prop.py}
\newpage
\lstinputlisting[language=python]{./test.py}


\end{document}